quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-20 paper-quollr.Rmd
Figure 6 need to find a way to remove row-wise gap

htmltools::browsable(
  tagList(
    tags$div(
      id = "fig-limb-model",  # This is the anchor
      crosstalk::bscols(
        htmltools::div(
          style = "display: grid; grid-template-columns: 1fr 1fr;",
          trimesh_limb_int,
          htmltools::div(style = "margin-top: 13px;", limb_highd_vis),
          trimesh_limb_best_int,
          htmltools::div(style = "margin-top: 13px;", limb_highd_vis_best),
        ),
        device = "xs"
      ),
      tags$p(tags$strong("Figure 6:"), "Compare the published.")
    )
  )
)

>>>>

```{r, eval=knitr::is_html_output()}
htmltools::browsable(
  htmltools::tagList(
    tags$div(
      id = "fig-limb-model",  # Anchor for referencing
      style = "text-align: center; margin-bottom: 1em;",

      # 2x2 grid layout
      htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr; row-gap: 0px; justify-items: center;",
        trimesh_limb_int,
        htmltools::div(style = "margin-top: 13px;", limb_highd_vis),
        trimesh_limb_best_int,
        htmltools::div(style = "margin-top: 13px;", limb_highd_vis_best)
      ),

      # Caption
      tags$p(
        tags$strong("Figure 6:"), 
        " Comparison of the published model with the best selected model."
      )
    )
  )
)
